A Comparison of Use-Case Based and Checklist- Based Reading: A Controlled Experiment

### 2015-03-10 rmtw/a4/latex8.tex
Added Title
sad

\title{Assignment 4}

@@

\Section{Acknowledgements}
U w0T m8

>>>>

\title{A Comparison of Use-Case Based and Checklist-
Based Reading: A Controlled Experiment}

@@

\Section{Acknowledgement}
John had the main responsibility for sections 3.2, 4.2. William had the main responsibility for sections 3.1, 4.1. The research questions were written together. We have, however, worked on all sections jointly - and all sections have been reviewed by both William and John. The testing has been done using a ``pair-testing'' approach.

Note: We were a bit unsure whether to only analyse the tests with help of the p-value or analysing the p-value together with test result and critical-value was the correct. We decided to do the latter and would like feedback on this.
